---
title: '<span style="font-size:48pt;">Preregistration</span>'
subtitle: '📈    👩🏻‍🔬️   📋 ' 
author: 'EDRS Open Science Pre-Conference Workshop'
date: 'Shirley B. Wang &emsp; &emsp; September 17, 2021'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      beforeInit: "macros.js"
      slideNumberFormat: "%current% / %total%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
    self_contained: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(
  base_color = "#23395b",
  footnote_font_size = "20px",
  footnote_color = "gray",
  text_slide_number_font_size = "18px"
)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_tachyons()
xaringanExtra::use_clipboard()
```

```{r packages, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(countdown)
library(patchwork)
```
class: onecol

<style type="text/css">
.onecol {
    font-size: 26px;
}
.twocol {
  font-size: 24px;
}
.remark-code {
  font-size: 24px;
  border: 1px solid grey;
}
a {
  background-color: lightblue;
}
.remark-inline-code {
  background-color: white;
}
</style>

## Today's Topics

Provide a brief introduction to **preregistration**. What is it, how and when should we do it, and why should we care?

Overview of common preregistration **templates and websites** (e.g., Open Science Framework, AsPredicted), including templates for secondary data analysis.

Address common **concerns and questions** about preregistration (e.g., "what if someone scoops my ideas?").

Provide you with enough knowledge to start pre-registering your own studies!

---
class: inverse, center, middle
# What is Pre-Registration?

---
class: onecol

## Pre-Registration Basics

Pre-registrations are ![:emphasize](time-stamped research plans) that are typically created **before** starting data collection<sup>1</sup>. 

.footnote[
[1] However, there are preregistration templates available for secondary data collection.
]

--

There are many templates available on the [Open Science Framework](https://osf.io/zab38/wiki/home/); they vary in specificity/length but typically include: 
- Study information
- Specific hypotheses
- Methods (inclusion/exclusion criteria, variables collected, sample size)
- Specific analysis plan
- Whether data collection has begun (and if so, whether you have looked at the data)

--

Note: **clinical trials** have specific requirements (dictated by government, funding agencies, etc).

---
class: inverse, center, middle

# Common Pre-Registration Templates

---
class: onecol

## Standard OSF Registration



